---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# {badgr}

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
<!-- badges: end -->

The goal of {badgr} is to use R to generate URL endpoints for [shields.io](https://shields.io/) metadata badges that you can use in your repository's README file or elsewhere.

I'm not affiliated with the excellent [shields.io](https://shields.io/).

You can [donate to or back shields.io](https://opencollective.com/shields) and can find out more from their:

* [website](https://shields.io/)
* [Twitter](https://twitter.com/Shields_io)
* [Discord](https://discord.com/invite/HjJCwm5)
* [source code](https://github.com/badges/shields)

## Installation

You can install {badgr} from GitHub with:

```{r}
remotes::install_github("matt-dray/badgr")
```

It's a work in progress and there are no guarantees.

## Example

This is a basic example that shows you how to generate the simplest possible badge.

```{r}
library(badgr)

badge <- get_badge_static(
  "Left bit", "Right bit", "blue",
  to_clipboard = FALSE,  # don't copy to clipboard
  open_browser = FALSE  # don't send to browser
)
```

The output looks like this:

```{r}
badge
```

Which when rendered, looks like this:

![](https://img.shields.io/badge/Left bit-Right bit-blue)

By default:

* the endpoint will be opened in your browser (`open_browser = TRUE`)
* Markdown notation for displaying the badge (`![]()`) will be added (`add_markdown = TRUE`)
* the whole string added to your clipboard (`to_clipboard = TRUE`)

## Code of Conduct

Please note that the {badgr} project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
